|

### 2021-03-08 supplementary_information_science.Rmd
Update supplementary_information_science.Rmd

We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]). We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area). The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazaki2015]. Watershed area was estimated based on the delineated watershed polygons. We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$. A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$. We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019]. We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmans2005]. We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhorn2020]. We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehner2011]. We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018], 'raster' [@hijmans2020], 'rgdal' [@rogerbivand2020], 'stars' [@edzerpebesma2020], and 'exactextractr' [@danielbaston2020].

>>>>

We collected data for watershed characteristics (watershed area [km^2^], branching probability, and mean elevation [m]), climatic variables (mean annual air temperature [degree Celsius] and cumulative precipitation [mm]), and land use (the fractions of forest, urban, and agriculture, and dam density per watershed area [km^-2^]). We used Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019] to delineate watershed polygons and river lines (defined as $\ge$ 1 km^2^ in the watershed area), which were separated by either the ocean, large lakes/reservoirs ($\ge$ 10 km^2^ in the areal area), or large rivers ($\ge$ 5000 km^2^ in the watershed area). The ocean and large lakes/reservoirs were extracted from Global 1-second Water Body Map ver 1.0 [@yamazaki2015]. Watershed area was estimated based on the delineated watershed polygons. We estimated branching probability by fitting exponential distributions to histograms of branch length (unit: kilometer, river segment between successive confluences or a confluence and the outlet/upstream terminal) as $branch~length \sim Exp(\lambda)$. A derived statistical quantity $1 − e^{−\lambda}$ corresponds to the theoretical branching probability $P_b$. We obtained the mean elevations for each watershed polygon using Hydrologically Adjusted Elevations of MERIT Hydro [@yamazaki2019]. We estimated the spatial averages of mean annual air temperature and cumulative precipitation for each watershed (\~1 km resolution), which were extracted from WorldClim 1.4 [@hijmans2005]. We calculated the fractions of forest, urban, and agriculture for each watershed using land use data in 2015 from Copernicus Global Land Service (100-m resolution) [@marcelbuchhorn2020]. We calculated dam density per watershed area (km^-2^) based on the Global Reservoir and Dam Database, Version 1 (GRanDv1) [@lehner2011]. We used ArcMap 10.7, SAGA 6.3.0, and the following R packages to perform geospatial analysis: 'RSAGA' [@brenning2018], 'sf' [@pebesma2018] 'raster' [@hijmans2020] 'stars' [@pebesma2020], and 'exactextractr' [@baston2020].
